---
title: "Week 9 Assignment - Web APIs"
author: "Stefano Biguzzi"
date: "10/19/2020"
output:
  html_document:
    highlight: pygments
    theme: cerulean
    toc: true
    toc_float: true
    code_folding: show
  pdf_document: default
editor_options: 
  chunk_output_type: console
params:
  key:
    label: "Please Enter NYTimes Book API Key"
    value: "5AOk4HOe2eMJmO23EvrSplQGGl7WVLtG"
    input: password
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# <span style="color: #969696;">Introduction

<span style="color: #969696;">Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.</span>

# Loading Libraries
The following libraries are required for running this code
```{r, message=F,warning=F}
library(glue)
library(httr)
library(jsonlite)
library(knitr)
```

# NY Times books API
I decided to use the NY Times books API, which gives the user data on book rankings by category or what they call list, for a given week. It's the data that comprises makes up their [Best Seller List](https://www.nytimes.com/books/best-sellers/).

## Construct URL
First we want to construct the URL so we pull the data we want with the parameters we want. 
```{r}
url_string = "https://api.nytimes.com/svc/books/v3/lists/{date}/{list}.json?api-key={api_key}"
```
The parameters include `date`, `list`, and `api_key`. For the purposes of this assignment I used the last day before the COVID-19 lockdown in New York, the list of books was *hardcover-nonfiction* and my api-key.
```{r}
api_key <- params$key
list <- "hardcover-nonfiction"
date <- "2020-03-14"
```
For the `list` parameter you could choose from the following options:  
```{r, echo=F,results='asis',comment=NA}
names <- fromJSON(rawToChar(GET("https://api.nytimes.com/svc/books/v3/lists/names.json?api-key=5AOk4HOe2eMJmO23EvrSplQGGl7WVLtG")$content))

list_names <- names$results

list1 <- head(list_names$list_name_encoded,20)
list2 <- list_names[21:40,"list_name_encoded"]
list3 <- tail(list_names$list_name_encoded,19)

kable(list(list(list1,list2),list3))
```

## Reading data from API
When we first read the `raw.data`, we get some information about the link as well as the link *results*. From the *results* list we can grab the *books* data frame.
```{r}
raw.data <- fromJSON(rawToChar(GET(glue(url_string))$content))
book.data <- raw.data$results$books
```

## Creating an R DataFrame
Finally we can simplify the book data frame that the API gives us to a data frame with the information we want in it.
```{r}
book.rank.df <-
  book.data[,c("rank",
               "rank_last_week",
               "weeks_on_list",
               "title",
               "author",
               "description",
               "primary_isbn13")]
```
The final result
```{r, echo=F, results='asis'}
kable(head(book.rank.df,5),caption = "Top 5 NYTimes Ranked Hardcover Nonfiction Books for the week of 2020-03-09")
```


